Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-02-02 grove-paper.tex
add constructor args to constructor-arity-sort map
clean up decomp example diagram

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P \times \{Exp, Pat, Typ\}) \\
      \hline
      \arity(\Root)={} & \left\{ \Root \right\} \\
      \arity(\PatVar)={} & \left\{ \right\} \\
      \arity(\ExpVar)={} & \left\{ \right\} \\
      \arity(\ExpLam)={} & \left\{ (\mathtt{Param}, Pat), (\mathtt{Type}, Typ), (\mathtt{Body}, Exp) \right\} \\
      \arity(\ExpApp)={} & \left\{ (\mathtt{Fun}, Exp), (\mathtt{Arg}, Exp) \right\} \\
      \arity(\ExpPlus)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpTimes)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpNum)={} & \left\{ \right\} \\
      \arity(\TypArrow)={} & \left\{ (\mathtt{Arg}, Typ), (\mathtt{Result}, Typ) \right\} \\
      \arity(\TypNum)={} & \left\{ \right\} \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (0cm,0cm) graph[graph style] {
      root[root style] -> {
       a/{\vWrapPlus} [> "\eWrapPlus"] -> {
        "\vSimpleTimes" [> "\eNestedPartsBob"'] -> {
         {},
         b/"\vNestedPartsAlice" [> "\eMultiParentAlice"', >merge edge]
        },
        {}
       }
      },
    };
    \path [draw,->,merge edge] (a) to ["\eMultiParentBob",out=-60,in=60] (b);
    \path (1cm,-1cm) graph[graph style] { plus/"\vSimpleTimes" };
    \path (2cm,-1cm) graph[graph style] { times/"\vMultiCycleTimes" };
    \path (2cm,-2cm) graph[graph style] { plus2/"\vSimpleTimes" };
    \path[draw,->,merge edge] (times) to ["\eMultiCycleBobTimes"'anchor=north,out=-135,in=-45] (plus);
    \path[draw,->,merge edge] (plus) to ["\eMultiCycleBobPlus"anchor=south,out=45,in=135] (times);
    \path[draw,->,merge edge] (times) to ["\eMultiCycleBobPlus"anchor=west,out=-90,in=90] (plus2);
    \path (1.5cm,-2.5cm) graph[graph style] { plus/"\vSimpleTimes" };
  \end{tikzpicture}
  \caption{Caption goes here}%
  \label{fig:Decomposition example}
\end{figure}

>>>>

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P \times \{Exp, Pat, Typ\}) \\
      \hline
      \arity(\Root)={} & \left\{ \Root \right\} \\
      \arity(\PatVar(x))={} & \left\{ \right\} \\
      \arity(\ExpVar(x))={} & \left\{ \right\} \\
      \arity(\ExpLam)={} & \left\{ (\mathtt{Param}, Pat), (\mathtt{Type}, Typ), (\mathtt{Body}, Exp) \right\} \\
      \arity(\ExpApp)={} & \left\{ (\mathtt{Fun}, Exp), (\mathtt{Arg}, Exp) \right\} \\
      \arity(\ExpPlus)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpTimes)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpNum(n))={} & \left\{ \right\} \\
      \arity(\TypArrow)={} & \left\{ (\mathtt{Arg}, Typ), (\mathtt{Result}, Typ) \right\} \\
      \arity(\TypNum)={} & \left\{ \right\} \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

\newvertex{DecompPlusA}{+}
\newedge{DecompTimesA}{L}
\newvertex{DecompTimesA}{*}
\newedge{DecompPlusAX}{R}
\newvertex{DecompX}{x}
\newedge{DecompTimesAX}{R}
%
\newedge{DecompPlusB}{L}
\newvertex{DecompPlusB}{+}
\newedge{DecompTimesB}{R}
\newvertex{DecompTimesB}{*}
\newedge{DecompY}{R}
\newvertex{DecompY}{y}
\newedge{DecompZ}{R}
\newvertex{DecompZ}{z}
%
\newedge{DecompTimes}{L}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (0cm,0cm) graph[graph style] {
      root[root style] -> {
       a/{\vDecompPlusA} [> "\eSimpleTimes"] -> {
        "\vDecompTimesA" [> "\eDecompTimesA"'] -> {
         {},
         b/"\vDecompX" [> "\eDecompTimesAX"']
        },
        {}
       }
      },
    };
    \path [draw,->] (a) to ["\eDecompPlusAX",out=-60,in=60] (b);
    %
    \path (2cm,-0.85cm) graph[graph style] { plus/"\vDecompPlusB" };
    \path (3cm,-0.85cm) graph[graph style] { times/"\vDecompTimesB" };
    \path (3.25cm,-1.75cm) graph[graph style] { y/"\vDecompY" };
    \path[draw,->] (times) to ["\eDecompPlusB"'anchor=north,out=-135,in=-45] (plus);
    \path[draw,->] (plus) to ["\eDecompTimesB"anchor=south,out=45,in=135] (times);
    \path[draw,->] (times) to ["\eDecompY"anchor=west] (y);
    %
    \path (1.55cm,-2.1cm) graph[graph style] { plus/"\vDecompZ" };
  \end{tikzpicture}
  \caption{Caption goes here}%
  \label{fig:Decomposition example}
\end{figure}
